# Mortality deviation compared with adjacent ages, years {#mortdevageyear}
```{r pb11, include=FALSE}
if(usingShiny==1){
  progress$set(detail="Mortality deviation",value = 11/18)
}
```

Chart of mortality deviations compared with adjacent ages. Note that the number of neighboring ages and/or years as well as the p-values for $X$ and the size of $R$ can be modified in the call to the script.

Expect to see large negative deviations at age 1 versus age 0. Patterns of large deviations, e.g., at ages ending in "0" or "5", may indicate problematic places in the mortality surface.

## Females
```{r intplsmortalitydeviationsF, cache=TRUE, fig.cap='Mortality deviation compared with adjacent ages, years',  fig.align='center',  fig.height=10, out.width="95%",fig.asp=1, dpi=150, warning=FALSE,  message=FALSE}
intpls_mortalitydeviations(parms, sex = "f", lagx=1, lagt=0, pvalX=0.001, crit1R=0.1, crit2R=0.05)
```

## Males
```{r intplsmortalitydeviationsM, cache=TRUE, fig.cap='Mortality deviation compared with adjacent ages, years',  fig.align='center',  fig.height=10, out.width="95%",fig.asp=1, dpi=150, warning=FALSE,  message=FALSE}
intpls_mortalitydeviations(parms, sex = "m", lagx=1, lagt=0, pvalX=0.001, crit1R=0.1, crit2R=0.05);
```
